---
title: "CNN Image Classification Model - Performance Report"
subtitle: "Github Profile Analysis"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
    number_sections: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 10, fig.height = 6)
library(tidyverse)
library(pROC)
library(ggplot2)
library(dplyr)
lapply(list.files("./R", full.names = TRUE), source)
```

# Executive Summary

This report presents the performance evaluation of the CNN image classification model trained on Github profile features. The model is designed to classify nodes based on their feature representations transformed into 6x6 grayscale images.

---

# 1. Model Comparison

```{r model-config}
targets::tar_load(cnn_models)

# Create comparison table - cnn_models is a list from pattern mapping
model_list <- if (is.list(cnn_models) && !is.data.frame(cnn_models)) {
  if ("model_name" %in% names(cnn_models)) {
    list(cnn_models)  # Single result, wrap it
  } else {
    cnn_models  # Multiple results from pattern
  }
} else {
  list(cnn_models)
}

comparison_df <- data.frame(
  Model = sapply(model_list, function(x) paste0("Epochs_", x$epochs)),
  Train_Accuracy = sapply(model_list, function(x) x$train_accuracy),
  Test_Accuracy = sapply(model_list, function(x) x$test_accuracy),
  Test_F1 = sapply(model_list, function(x) x$test_metrics$f1),
  Test_AUC = sapply(model_list, function(x) {
    if (!is.null(x$test_results)) {
      tryCatch({
        roc_obj <- pROC::roc(x$test_results$actual, x$test_results$probability, quiet = TRUE)
        as.numeric(pROC::auc(roc_obj))
      }, error = function(e) NA)
    } else {
      NA
    }
  })
)

knitr::kable(comparison_df, caption = "Model Performance Comparison by Epochs")
```

**Model Architecture:**
- Input: 6x6 grayscale images
- Conv Layer 1: 1 → 16 filters (3x3 kernel, ReLU, Max Pool)
- Conv Layer 2: 16 → 32 filters (3x3 kernel, ReLU, Max Pool)
- FC Layer 1: 32 → 64 neurons (ReLU, Dropout 0.3)
- FC Layer 2: 64 → 1 neuron (Binary output)
- Loss: MSE
- Optimizer: Adam (lr=0.001)

---

# 2. Prediction Summary

```{r metrics}
targets::tar_load(single_prediction)
predictions_df <- safe_extract_predictions(single_prediction)

if (!is.null(predictions_df)) {
  summary_df <- data.frame(
    Metric = c("Total Predictions", "Positive (1)", "Negative (0)", 
               "Mean Probability", "Min Probability", "Max Probability"),
    Value = c(
      nrow(predictions_df),
      sum(predictions_df$prediction, na.rm = TRUE),
      sum(predictions_df$prediction == 0, na.rm = TRUE),
      round(mean(predictions_df$probability, na.rm = TRUE), 4),
      round(min(predictions_df$probability, na.rm = TRUE), 4),
      round(max(predictions_df$probability, na.rm = TRUE), 4)
    ),
    stringsAsFactors = FALSE
  )
  
  knitr::kable(summary_df, caption = "Prediction Summary Statistics")
} else {
  cat("No valid prediction data available.\n")
}
```

---

# 3. ROC Curve Analysis

## Test Data ROC Comparison

```{r roc-test-comparison}
roc_data <- list()

for (model_res in model_list) {
  model_name <- paste0("Epochs_", model_res$epochs)
  res <- model_res$test_results
  if (!is.null(res)) {
    # Ensure we have both classes
    if (length(unique(res$actual)) > 1) {
      tryCatch({
        roc_obj <- pROC::roc(res$actual, res$probability, quiet = TRUE)
        roc_data[[model_name]] <- roc_obj
      }, error = function(e) {})
    }
  }
}

if (length(roc_data) > 0) {
  ggroc(roc_data) +
    geom_segment(aes(x = 1, xend = 0, y = 0, yend = 1), color="grey", linetype="dashed") +
    theme_minimal() +
    labs(title = "ROC Curves on Test Data", color = "Model")
} else {
  plot.new()
  text(0.5, 0.5, "No valid results for ROC (need both classes)", cex = 1.5)
}
```

```{r roc-stats}
# Display detailed stats for the best model (highest AUC)
if (exists("comparison_df") && nrow(comparison_df) > 0) {
  best_model_idx <- which.max(comparison_df$Test_AUC)
  if (length(best_model_idx) > 0) {
    best_model_name <- comparison_df$Model[best_model_idx]
    cat(paste("Best Model based on AUC:", best_model_name, "\n"))
  }
}
```

---

# 4. Prediction Probability Distribution

```{r dist}
if (!is.null(predictions_df)) {
  plot_prediction_distribution(predictions_df)
} else {
  plot.new()
  text(0.5, 0.5, "No data for distribution plot", cex = 1.5)
}
```

---

# 4. Sample Predictions

```{r sample}
if (!is.null(predictions_df)) {
  cols_to_show <- c("image_id", "prediction", "probability")
  if ("raw_output" %in% names(predictions_df)) {
    cols_to_show <- c(cols_to_show, "raw_output")
  }
  
  knitr::kable(
    head(predictions_df[, cols_to_show], 20),
    caption = "Sample Predictions"
  )
} else {
  cat("Cannot display predictions - data not in expected format\n")
}
```

---

# 5. Recommendations & Conclusions

## Key Findings

- Model predictions generated for batch query
- Probability distribution shows model confidence across predictions
- Consider threshold optimization based on business requirements

## Next Steps

1. Validate predictions with ground truth labels when available
2. Perform cross-validation for robustness assessment
3. Consider threshold optimization based on business requirements
4. Explore ensemble methods for improved performance
5. Implement monitoring for model drift detection

---

*Report generated on `r Sys.time()`*

```{r session-info}
sessionInfo()
```

---

*Report generated on `r Sys.time()`*
