---
title: "CNN Image Classification Model - Performance Report"
subtitle: "Github Profile Analysis"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
    number_sections: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.width = 10, fig.height = 6)

# Load required libraries
library(tidyverse)
library(caret)
library(pROC)
library(DET)
library(ggplot2)
library(dplyr)

# Source helper functions
lapply(list.files("./R", full.names = TRUE), source)
```

# Executive Summary

This report presents the performance evaluation of the CNN image classification model trained on Github profile features. The model is designed to classify nodes based on their feature representations transformed into 6x6 grayscale images.

---

# 1. Model Configuration & Data

```{r model-config, eval=FALSE}
# Load targets results
targets::tar_load(cnn_model)
targets::tar_load(test_single_prediction)
targets::tar_load(single_prediction)

# Model architecture:
# - Input: 6x6 grayscale images
# - Conv Layer 1: 1 → 16 filters (3x3 kernel, ReLU, Max Pool)
# - Conv Layer 2: 16 → 32 filters (3x3 kernel, ReLU, Max Pool)
# - FC Layer 1: 32 → 64 neurons (ReLU, Dropout 0.3)
# - FC Layer 2: 64 → 1 neuron (Binary output)
# - Loss: MSE
# - Optimizer: Adam (lr=0.001)
```

**Training Parameters:**
- Epochs: 2
- Batch Size: 16
- Learning Rate: 0.001
- Threshold: 0.5

---

# 2. Performance Metrics

```{r performance-metrics, eval=FALSE}
# This section loads predictions and calculates metrics
# predictions <- tar_read(single_prediction)

# Create confusion matrix
calculate_metrics <- function(actual, predicted) {
  cm <- confusionMatrix(factor(predicted), factor(actual))
  
  metrics <- list(
    accuracy = cm$overall['Accuracy'],
    sensitivity = cm$byClass['Sensitivity'],
    specificity = cm$byClass['Specificity'],
    precision = cm$byClass['Pos Pred Value'],
    f1 = cm$byClass['F1'],
    balanced_accuracy = cm$byClass['Balanced Accuracy']
  )
  
  return(metrics)
}
```

```{r metrics-table}
# Performance Metrics Summary
metrics_df <- data.frame(
  Metric = c("Accuracy", "Sensitivity (Recall)", "Specificity", "Precision", "F1-Score", "Balanced Accuracy"),
  Value = c(NA, NA, NA, NA, NA, NA),
  stringsAsFactors = FALSE
)

knitr::kable(metrics_df, caption = "Model Performance Metrics")
```

---

# 3. ROC Curve Analysis

```{r roc-curve, eval=FALSE}
# ROC Curve Calculation and Visualization
roc_curve <- function(actual, predicted_probs) {
  roc_obj <- roc(actual, predicted_probs, 
                 levels = c(0, 1), direction = "<")
  return(roc_obj)
}

# Example ROC curve plot
ggplot_roc <- function(roc_obj) {
  roc_df <- data.frame(
    fpr = 1 - roc_obj$specificities,
    tpr = roc_obj$sensitivities
  )
  
  ggplot(roc_df, aes(x = fpr, y = tpr)) +
    geom_path(linewidth = 1, color = "#2E86AB") +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "gray") +
    labs(
      title = "ROC Curve",
      x = "False Positive Rate",
      y = "True Positive Rate",
      subtitle = paste0("AUC = ", round(roc_obj$auc, 3))
    ) +
    theme_minimal() +
    theme(
      plot.title = element_text(face = "bold", size = 14),
      plot.subtitle = element_text(size = 12)
    )
}
```

```{r roc-plot}
# ROC Curve Placeholder
plot.new()
text(0.5, 0.5, "ROC Curve\n(Requires prediction data)", 
     cex = 2, col = "gray50", adj = c(0.5, 0.5))
```

**AUC Value:** [To be calculated from predictions]

---

# 4. DET Curve Analysis

```{r det-curve, eval=FALSE}
# Detection Error Tradeoff (DET) Curve
det_curve <- function(actual, predicted_probs) {
  # DET curve shows false negative rate vs false positive rate
  # Generated using DET package
  
  # Create ROC object for DET visualization
  roc_obj <- roc(actual, predicted_probs)
  
  # Extract rates
  fnr <- 1 - roc_obj$sensitivities  # False Negative Rate
  fpr <- 1 - roc_obj$specificities  # False Positive Rate
  
  return(list(fnr = fnr, fpr = fpr))
}
```

```{r det-plot}
# DET Curve Placeholder
plot.new()
text(0.5, 0.5, "DET Curve\n(Requires prediction data)", 
     cex = 2, col = "gray50", adj = c(0.5, 0.5))
```

**DET Curve Interpretation:**
- Shows the tradeoff between False Negative Rate and False Positive Rate
- Lower curves indicate better performance
- Operating point selection based on application requirements

---

# 5. AUC Analysis

```{r auc-analysis}
# Area Under the Curve (AUC) Summary
auc_summary <- data.frame(
  Metric = c("AUC", "95% CI Lower", "95% CI Upper", "Interpretation"),
  Value = c("TBD", "TBD", "TBD", "To be calculated from test predictions")
)

knitr::kable(auc_summary, caption = "AUC Statistics")
```

**AUC Interpretation Guide:**
- 0.90 - 1.00: Excellent discrimination
- 0.80 - 0.90: Good discrimination
- 0.70 - 0.80: Fair discrimination
- 0.60 - 0.70: Poor discrimination
- 0.50 - 0.60: Fail discrimination

---

# 6. Variable Importance

```{r variable-importance, eval=FALSE}
# Feature Importance Analysis
# For CNN models, importance can be derived from:
# 1. Layer activation analysis
# 2. Gradient-based importance
# 3. Feature attribution methods

get_feature_importance <- function(model) {
  # Extract weights from model layers
  # This would require custom implementation based on torch model
  
  importance <- data.frame(
    layer = c("Conv1 Filters", "Conv2 Filters", "FC1 Weights"),
    mean_weight = c(NA, NA, NA),
    std_weight = c(NA, NA, NA)
  )
  
  return(importance)
}
```

```{r importance-plot}
# Variable Importance Plot
importance_df <- data.frame(
  Feature = c("Conv Layer 1", "Conv Layer 2", "FC Layer 1"),
  Importance = c(NA, NA, NA),
  stringsAsFactors = FALSE
)

ggplot(importance_df, aes(x = reorder(Feature, Importance), y = Importance)) +
  geom_col(fill = "#2E86AB", alpha = 0.8) +
  coord_flip() +
  labs(
    title = "Feature/Layer Importance",
    x = "Layer",
    y = "Importance Score"
  ) +
  theme_minimal() +
  theme(plot.title = element_text(face = "bold"))
```

```{r importance-table}
knitr::kable(importance_df, caption = "Layer Importance Scores")
```

---

# 7. Confusion Matrix

```{r confusion-matrix, eval=FALSE}
# Confusion Matrix Visualization
confusion_matrix <- caret::confusionMatrix(predicted, actual)

# Create heatmap
cm_df <- as.data.frame(confusion_matrix$table)

ggplot(cm_df, aes(x = Prediction, y = Reference, fill = Freq)) +
  geom_tile() +
  geom_text(aes(label = Freq), color = "white", size = 5) +
  scale_fill_gradient(low = "lightblue", high = "#2E86AB") +
  labs(title = "Confusion Matrix") +
  theme_minimal()
```

---

# 8. Predictions Detail

```{r predictions-detail, eval=FALSE}
# Show detailed predictions with confidence intervals
predictions_detail <- tar_read(single_prediction)

if (!is.null(predictions_detail)) {
  knitr::kable(
    head(predictions_detail, 20),
    caption = "Sample Predictions with Probabilities"
  )
}
```

---

# 9. Model Diagnosis

## Training Convergence

```{r training-convergence}
plot.new()
text(0.5, 0.5, "Training Convergence Plot\n(Loss over epochs)", 
     cex = 2, col = "gray50", adj = c(0.5, 0.5))
```

## Class Distribution

```{r class-distribution}
class_dist <- data.frame(
  Class = c("Negative (0)", "Positive (1)"),
  Count = c(NA, NA),
  Percentage = c(NA, NA)
)

ggplot(class_dist, aes(x = Class, y = Count, fill = Class)) +
  geom_col(alpha = 0.8) +
  geom_text(aes(label = paste0(Percentage, "%")), vjust = -0.5) +
  scale_fill_manual(values = c("#A23B72", "#2E86AB")) +
  labs(title = "Target Class Distribution", y = "Count") +
  theme_minimal() +
  theme(legend.position = "none", plot.title = element_text(face = "bold"))
```

---

# 10. Recommendations & Conclusions

## Key Findings

- Model performance to be evaluated on held-out test set
- ROC/DET curves provide guidance for threshold optimization
- Consider application-specific requirements (sensitivity vs specificity tradeoff)

## Next Steps

1. Evaluate on full validation set
2. Perform cross-validation for robustness assessment
3. Consider threshold optimization based on business requirements
4. Explore ensemble methods for improved performance
5. Implement monitoring for model drift detection

---

# Appendix: Session Information

```{r session-info}
sessionInfo()
```

---

*Report generated on `r Sys.time()`*
