---
title: "CNN Image Classification Model - Performance Report"
subtitle: "Github Profile Analysis"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
    number_sections: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 10, fig.height = 6)
library(tidyverse)
library(pROC)
library(ggplot2)
library(dplyr)
lapply(list.files("./R", full.names = TRUE), source)
```

# Executive Summary

This report presents the performance evaluation of the CNN image classification model trained on Github profile features. The model is designed to classify nodes based on their feature representations transformed into 6x6 grayscale images.

---

# 1. Model Configuration & Data

```{r model-config}
targets::tar_load(cnn_model)

# Extract metrics from trained model
train_metrics <- cnn_model$metrics
train_accuracy <- cnn_model$accuracy
```

**Training Parameters:**
- Epochs: 2
- Batch Size: 16
- Learning Rate: 0.001
- Threshold: 0.5

**Model Architecture:**
- Input: 6x6 grayscale images
- Conv Layer 1: 1 → 16 filters (3x3 kernel, ReLU, Max Pool)
- Conv Layer 2: 16 → 32 filters (3x3 kernel, ReLU, Max Pool)
- FC Layer 1: 32 → 64 neurons (ReLU, Dropout 0.3)
- FC Layer 2: 64 → 1 neuron (Binary output)
- Loss: MSE
- Optimizer: Adam (lr=0.001)

**Training Performance:**
- Accuracy: `r round(train_accuracy, 4)`
- Sensitivity: `r round(train_metrics$sensitivity, 4)`
- Specificity: `r round(train_metrics$specificity, 4)`
- Precision: `r round(train_metrics$precision, 4)`
- F1 Score: `r round(train_metrics$f1, 4)`

---

# 2. Prediction Summary

```{r metrics}
targets::tar_load(single_prediction)
predictions_df <- safe_extract_predictions(single_prediction)

if (!is.null(predictions_df)) {
  summary_df <- data.frame(
    Metric = c("Total Predictions", "Positive (1)", "Negative (0)", 
               "Mean Probability", "Min Probability", "Max Probability"),
    Value = c(
      nrow(predictions_df),
      sum(predictions_df$prediction, na.rm = TRUE),
      sum(predictions_df$prediction == 0, na.rm = TRUE),
      round(mean(predictions_df$probability, na.rm = TRUE), 4),
      round(min(predictions_df$probability, na.rm = TRUE), 4),
      round(max(predictions_df$probability, na.rm = TRUE), 4)
    ),
    stringsAsFactors = FALSE
  )
  
  knitr::kable(summary_df, caption = "Prediction Summary Statistics")
} else {
  cat("No valid prediction data available.\n")
}
```

---

# 3. ROC Curve Analysis

## Training Data ROC

```{r roc-train}
if (!is.null(cnn_model$results)) {
  plot_roc(cnn_model$results$actual, cnn_model$results$probability)
} else {
  plot.new()
  text(0.5, 0.5, "No training results available for ROC", cex = 1.5)
}
```

## Test Data ROC

```{r roc-test}
if (!is.null(predictions_df) && !all(is.na(predictions_df$correct_answer))) {
  plot_roc(predictions_df$correct_answer, predictions_df$probability)
} else {
  plot.new()
  text(0.5, 0.5, "No ground truth labels available for Test ROC", cex = 1.5)
}
```

```{r roc-stats}
if (!is.null(predictions_df) && !all(is.na(predictions_df$correct_answer))) {
  roc_stats <- get_roc_stats(predictions_df$correct_answer, predictions_df$probability)
  if (!is.null(roc_stats)) {
    knitr::kable(roc_stats, caption = "Test Data AUC Statistics")
  }
}
```

---

# 4. Prediction Probability Distribution

```{r dist}
if (!is.null(predictions_df)) {
  plot_prediction_distribution(predictions_df)
} else {
  plot.new()
  text(0.5, 0.5, "No data for distribution plot", cex = 1.5)
}
```

---

# 4. Sample Predictions

```{r sample}
if (!is.null(predictions_df)) {
  cols_to_show <- c("image_id", "prediction", "probability")
  if ("raw_output" %in% names(predictions_df)) {
    cols_to_show <- c(cols_to_show, "raw_output")
  }
  
  knitr::kable(
    head(predictions_df[, cols_to_show], 20),
    caption = "Sample Predictions"
  )
} else {
  cat("Cannot display predictions - data not in expected format\n")
}
```

---

# 5. Recommendations & Conclusions

## Key Findings

- Model predictions generated for batch query
- Probability distribution shows model confidence across predictions
- Consider threshold optimization based on business requirements

## Next Steps

1. Validate predictions with ground truth labels when available
2. Perform cross-validation for robustness assessment
3. Consider threshold optimization based on business requirements
4. Explore ensemble methods for improved performance
5. Implement monitoring for model drift detection

---

*Report generated on `r Sys.time()`*

```{r session-info}
sessionInfo()
```

---

*Report generated on `r Sys.time()`*
