---
title: "CNN Image Classification Model - Performance Report"
subtitle: "Github Profile Analysis"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
    number_sections: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 10, fig.height = 6)
library(tidyverse)
library(pROC)
library(ggplot2)
library(dplyr)
lapply(list.files("./R", full.names = TRUE), source)
```

# Executive Summary

This report presents the performance evaluation of the CNN image classification model trained on Github profile features. The model is designed to classify nodes based on their feature representations transformed into 6x6 grayscale images.

---

# 1. Model Comparison

```{r model-config}
targets::tar_load(c(test_cnn_model_2, test_cnn_model_4, test_logistic_model_2, test_logistic_model_4))

# Create a named list of models
model_list <- list(
  CNN_2ep = c(test_cnn_model_2, list(name = "CNN_2ep")),
  CNN_4ep = c(test_cnn_model_4, list(name = "CNN_4ep")),
  Logistic_2ep = c(test_logistic_model_2, list(name = "Logistic_2ep")),
  Logistic_4ep = c(test_logistic_model_4, list(name = "Logistic_4ep"))
)

comparison_df <- data.frame(
  Model = sapply(model_list, function(x) x$name),
  Accuracy = sapply(model_list, function(x) x$metrics$accuracy),
  F1_Score = sapply(model_list, function(x) x$metrics$f1),
  Kappa = sapply(model_list, function(x) x$metrics$kappa),
  AUC = sapply(model_list, function(x) {
    results_df <- if (!is.null(x$results)) x$results else x$test_results
    if (!is.null(results_df)) {
      tryCatch({
        roc_obj <- pROC::roc(results_df$actual, results_df$probability, quiet = TRUE)
        as.numeric(pROC::auc(roc_obj))
      }, error = function(e) NA)
    } else {
      NA
    }
  })
)

knitr::kable(comparison_df, caption = "Model Performance Comparison")
```

---

# 2. Confusion Matrix Analysis

```{r confusion-matrix, fig.width=8, fig.height=6}
# Display confusion matrix for each model
if (exists("model_list") && length(model_list) > 0) {
  for (i in seq_along(model_list)) {
    model <- model_list[[i]]
    results_df <- if (!is.null(model$results)) model$results else model$test_results
    
    if (!is.null(results_df)) {
      cm_plot <- plot_confusion_matrix(results_df$actual, results_df$predicted)
      cm_plot <- cm_plot + ggtitle(paste("Confusion Matrix:", model$name))
      print(cm_plot)
      cat("\n\n") # Add spacing between plots
    }
  }
}
```

---

# 3. Prediction Summary



---

# 4. ROC and DET Curves

```{r echo=FALSE, fig.width=12, fig.height=6}
# Create DETs object from model_performance list
model_dets <- create_dets_object(model_list)

if (!is.null(model_dets)) {
  par(pty="s", mfrow=c(1,2))
  plotROCs(model_dets, xlim=c(0,1), ylab="True Positive Rate")
  plot(model_dets, main="DET Curves")
} else {
  cat("Unable to create DET curves - insufficient data\n")
}
```

---
---

# 7. Recommendations & Conclusions

## Key Findings

- Model predictions generated for batch query
- Probability distribution shows model confidence across predictions
- Consider threshold optimization based on business requirements

## Next Steps

1. Validate predictions with ground truth labels when available
2. Perform cross-validation for robustness assessment
3. Consider threshold optimization based on business requirements
4. Explore ensemble methods for improved performance
5. Implement monitoring for model drift detection

---

*Report generated on `r Sys.time()`*

```{r session-info}
sessionInfo()
```

---

*Report generated on `r Sys.time()`*
